\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Problem Statement: Chrome Dino Runner \\ \bigskip \large SFWRENG 3XA3 Project \\ \bigskip \large Team Number: L03 Group 1 \\ \large Team Name: ``Team Rex'' }

\author{Chelsea Maramot \\ maramotc \\ \\ Anjola Adewale \\ adewaa1 \\ \\ Sheridan Fong \\ fongs7 }


\begin{document}

\maketitle
\newpage

The current pandemic has abruptly disrupted the entertainment sector, such as the performing arts, sports, and many other related industries. People are seeking entertainment within the comfort of their homes. One such means that we propose is through video games. Specifically, we aim to redesign the classic Chrome T-Rex dinosaur game to improve its user-friendliness and interactivity, while maintaining the game’s basic functionality. The main objective of our implementation is to entertain the user at any time, not only while Chrome tries to reconnect to the internet.
\bigskip

Some of the current problems of the game include:


\begin{itemize}
    \item The lack of sound, which removes from the user experience. 
    \item The graphic design of the game is simple, but can be updated to a themed version. 
    \item There is a lack of certain features such as the “play again” button and an instructions page, which is an accessibility issue as it might not be intuitive to everyone that pressing a random key will restart the game.
    \item A lot of video game players are used to using WASD keys as arrow keys which are not supported in this implementation of the game.
    \item Does not implement software design principles such as information hiding and modularity. 
\end{itemize}

These problems all hinder the user experience. Solving these problems will make the game more user-friendly, interactive and engaging. The addition of instructions and additional keyboard commands will make the game easily comprehensible for new players. The implementation of the infamous Chrome Dinosaur game with high scores and different themes provides an opportunity for users to play the game without losing an internet connection and provides a nostalgic experience.

\bigskip

The key stakeholders for this problem are Chrome users who have access to a computer, the development team, and the course instructor and TAs. The users will play the game free of charge through a downloadable executable file that can be run on a computer.

\bigskip

The development team is Team Rex; we are responsible for the product life cycle, maintaining and implementing code. The course instructors and TAs act as the regulatory body of the project and clients, as we are meeting their internal deadlines and requirements. The project environment includes Python, PyGame, Windows OS, GIT version control and possibly Javascript. 


\end{document}
