\documentclass{article}
\usepackage[utf8]{inputenc}


\title{Development Plan: Chrome Dino Runner \\ \bigskip \large SFWRENG 3XA3 Project \\ \bigskip \large Team Number: L03 Group 1 \\ \large Team Name: ``Team Rex'' }

\author{Chelsea Maramot \\ maramotc \\ \\ Anjola Adewale \\ adewaa1 \\ \\ Sheridan Fong \\ fongs7 }

\date{February 2022}

\begin{document}
	
	\maketitle
	
	\section{Introduction}
	
	\section{Development Plan}
	
	\section{Team Meeting Plan}
	Team Rex will primarily be using Facebook and Microsoft teams to communicate.
	All members must respond to posts or messages in which they have been mentioned within 24 hours. All members will meet on Microsoft teams every Monday and Wednesday between the hours of 9:30 am - 11:20 pm. If we are unable to complete the week’s tasks during lab time, the group will decide on an additional date during the week to complete said tasks.
	
	During these meetings, each individual will have a role (Administrator, Chair and Coordinator) as outlined in Table x. The roles will rotate every week.
	
	
	\section{Team Member Roles}
	
	\section{Git Workflow Plan}
	
	\section{Proof of Concept Demonstration Plan}
	
	\section{Technology}
	The program will run on a computer that has Python and the library Pygame. 
	
	\section{Coding Style}
	This project will follow the PEP 8 style guide. The main objective of PEP is to enhance the consistency and readability of code. Using a standardized coding style amongst team members will keep the code cohesive and comprehendible as all variables, classes, and comments will be written in the same style. 
	
	\section{Project Schedule}
	
	\section{Project Review}
	
\end{document}
